\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-12-16 Papers/Stochastic_Uncertainty_Propagation_TPS/RebuttalRound1-TPWRS-01391-2021.tex

Following the same vein, there are some unnecessary information and technical points provided in this paper that may be distracting.
For example, on page 3, why would the authors mention the Kuramoto oscillator model?
On page 4, is the detailed discussion regarding Wasserstein-2 metric necessary? Similarly, on page 5, the discussion about the natural energy functional and how the gradient drift case does not apply also seems too detailed.}

{\nib \blue{TBD.}}

\noindent
{\bf R4.4. Comments by reviewer}:\\
{\em Along with [25], there are recent developments that over-approximates the reachable set for nonlinear systems under uncertain initial conditions, parameters, and external disturbances:
``Reach-Set Estimation for DAE Systems under Uncertainty and Disturbances Using Trajectory Sensitivity and Logarithmic Norm".}

{\nib \blue{Thanks for providing that interesting recent reference. We have cited the same in the revised manuscript.}}

@@

\noindent
{\bf R4.5. Comments by reviewer}:\\
{\em On page 7, the authors stated about ``To account the pertinent geometry of $\mathbb{T}^n \times \mathbb{R}^n$". What exactly does this mean? Do the authors indicate that in (28) the two groups of state values are independent? Or do the authors mean the specific choices of the product von Mises PDF and the uniform distribution? If so, what are the connections?}

{\nib \blue{We simply mean that the joint PDF should be supported on $\mathbb{T}^n \times \mathbb{R}^n$, or a submanifold thereof. For instance, one cannot assume the initial joint PDF to be a $2n$ dimensional multivariate normal since that is supported over $\mathbb{R}^{2n}$, not over $\mathbb{T}^n \times \mathbb{R}^n$. It is, however, perfectly fine if some or all of the $2n$ components of the initial state vector are statistically correlated. As long as the support is $\mathbb{T}^n \times \mathbb{R}^n$, there is no issue if the angular variables are correlated with the Euclidean (i.e., angular velocity) variables.}}

@@

\noindent
{\bf R4.6. Comments by reviewer}:\\
{\em On page 5, is there a mistake in ``random samples from (28), and evaluated at (28)"?}

{\nib \blue{That was not a typo. We meant that (28) was \ul{used in two ways}: it was used to generate initial state samples, and then the initial joint PDF values at those samples were evaluated via the functional form of (28), i.e., as in function evaluation. This is needed in our case because unlike standard Monte Carlo, we \ul{co-evolve} the state samples and joint PDF values at those state samples. \ul{To clarify this further, in the revised manuscript, we have slightly expanded that sentence}.}}

### 2021-12-16 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS_Rev1.tex
initiated TPS rebuttal version 1

In a different vein, \emph{deterministic bounded uncertainty models} for power flow simulations have been used \cite{dimitrovski2004boundary,hiskens2006sensitivity,chen2012method,althoff2014formal} for set-valued analysis. These, however, require approximating the underlying nonlinear differential algebraic equations (DAEs) appearing in power system dynamic simulation, and thus lead to conservative analysis. For example, the method in \cite{althoff2014formal} requires converting the nonlinear DAEs to linear DAEs in such a way that guarantees set-valued over-approximation of the reachable sets. Likewise, the convex optimization-based bounded uncertainty propagation methods in \cite{choi2017propagating,choi2018propagating} require second order approximation of the power flow state variables as function of the uncertainties.

@@

>>>>

In a different vein, \emph{deterministic bounded uncertainty models} for power flow simulations have been used \cite{dimitrovski2004boundary,hiskens2006sensitivity,chen2012method,althoff2014formal,geng2020reach} for set-valued analysis. These, however, require approximating the underlying nonlinear differential algebraic equations (DAEs) appearing in power system dynamic simulation, and thus lead to conservative analysis. For example, the method in \cite{althoff2014formal} requires converting the nonlinear DAEs to linear DAEs in such a way that guarantees set-valued over-approximation of the reachable sets. Likewise, the convex optimization-based bounded uncertainty propagation methods in \cite{choi2017propagating,choi2018propagating} require second order approximation of the power flow state variables as function of the uncertainties.

@@

{\blue{\bibitem{geng2020reach}
S.~Geng, and I.A.~Hiskens, ``Reach-Set Estimation for DAE Systems under Uncertainty and Disturbances Using Trajectory Sensitivity and Logarithmic Norm", \emph{21st IFAC World Congress}, Vol. 53, No. 2, pp. 1955--1961, 2020.}}
